---
title: "Project 3 - Example Main Script"
author: "Yuting Ma, Tian Zheng"
date: "February 24, 2016"
output:
  pdf_document: default
  html_document: default
---
In your final repo, there should be an R markdown file that organizes **all computational steps** for evaluating your proposed image classification framework. 

This file is currently a template for running evaluation experiments of image analysis (or any predictive modeling). You should update it according to your codes but following precisely the same structure. 

```{r}

if(!require("gbm")){
  install.packages("gbm")
}

library("gbm")
library(adabag)


```

```{r}
source("../lib/cross_validation.R")
source("../lib/train.R")
source("../lib/test.R")
```

```{r}
sift <- data.frame(t(read.csv("../data/sift_features.csv")))
y<-c(rep(0,1000),rep(1,1000))
s1<-data.frame(cbind(y,sift))
pca <- data.frame(read.csv("../output/feature_pca.csv"))
lasso<- data.frame(read.csv("../output/feature_lasso.csv"))
lasso<-lasso[,-1]
pca<-pca[,-1]

num<-apply(abs(sign(sift)),1,sum)
```





gbm!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
```{r warning=FALSE}
err<-rep(NA,20)
k<-3
for(i in 1:20){
  err[i]<-cv.function(pca,y,i,k)
}
```

```{r}
plot(err)
```
```{r}
 sift_gbm <- gbm.fit(x=sift, y=y,
                     n.trees=1000,
                     distribution="bernoulli",
                     interaction.depth=11, 
                     bag.fraction = 0.5,
                     verbose=FALSE)
```
```{r}

ada<-rpart(y~.,data=s1)
n<-names(ada$variable.importance)
select<-as.numeric(substr(n,2,nchar(n)))
f1<-cbind(pca,sift[,select])
```

```{r warning=FALSE}
err2<-rep(NA,20)
k<-3
for(i in 1:20){
  err2[i]<-cv.function(f1,y,i,k)
}
plot(err2)
```



```{r warning=FALSE}
err3<-rep(NA,20)
k<-3
cl <- makeCluster(getOption("cl.cores", 8))
err4 <- clusterApply(cl, 1:20,  cv.function,X.train=f1, y.train=y, K=k)
#for(i in 1:20){
#  err3[i]<-cv.function(sift[,select],y,i,k)
#}
err4<-unlist(err4)
plot(err4)

```


```{r warning=FALSE}
f2<-cbind(f1,lasso)
k<-3
cl <- makeCluster(getOption("cl.cores", 8))
err5 <- parLapply(cl, 1:20,  cv.function,X.train=f2, y.train=y, K=k)
#for(i in 1:20){
#  err3[i]<-cv.function(sift[,select],y,i,k)
#}
err5<-unlist(err5)
plot(err5)

```



knn!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

```{r}
library(e1071)
library(class)
p<-rep(NA,20)
for(i in 1:20){
  result<-knn.cv(f2,y,k=i)
  percent<-as.numeric(result==y)
  p[i]<-1-sum(percent)/2000
}
plot(p)

```


random forest!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
```{r}
library(data.table)
library(dplyr)
library(randomForest)
library(parallel)

 



### random forest test



rf.cv.function <- function(X.train, y.train,d,ntree=1000,mtry=sqrt(ncol(X.train)),K=5){
  source("../lib/train.R")
  source("../lib/test.R")
  n <- length(y.train)
  n.fold <- floor(n/K)
  s <- sample(rep(1:K, c(rep(n.fold, K-1), n-(K-1)*n.fold)))  
  cv.error <- rep(NA, K)
  
  for (i in 1:K){
    train.data <- X.train[s != i,]
    train.label <- y.train[s != i]
    test.data <- X.train[s == i,]
    test.label <- y.train[s == i]
    
    fit <- rf_train(train.data, train.label, ntree=ntree,mtry=mtry,node=d)
    pred <- rf_test(fit, test.data)  
    cv.error[i] <- mean(pred != test.label)  
    
  }			
  return(mean(cv.error))
}

t1<-Sys.time()
cl <- makeCluster(getOption("cl.cores", 8))

rderr <- parLapply(cl, 1:16,  rf.cv.function,X.train=f2, y.train=y, K=k)
rderr<-unlist(rderr)
plot(rderr)
t2<-Sys.time()
t2-t1
#index <- sample(1:2000,1800,replace = F)
#traindata <- data[index,]
#testdata <- data[-index,]
#trainlabel <- label[index]
#testlabel <- label[-index]
#model <- rf_train(traindata,trainlabel,ntree = 500,mtry=sqrt(ncol(traindata)))
#mean(rf_test(model,testdata)!=testlabel)


```

```{r}
f3<-cbind(num,f2)
t1<-Sys.time()
cl <- makeCluster(getOption("cl.cores", 8))

rderr2 <- parLapply(cl, 1:16,  rf.cv.function,X.train=f3, y.train=y, K=k)
rderr2<-unlist(rderr2)
plot(rderr2)
t2<-Sys.time()
t2-t1
```
```{r}
load("../output/feature0.Rdata")
feature0<-unlist(feature0)
f4<-cbind(feature0,f3)
t1<-Sys.time()
cl <- makeCluster(getOption("cl.cores", 8))

rderr3 <- parLapply(cl, 1:16,  rf.cv.function,X.train=f4, y.train=y, K=k)
rderr3<-unlist(rderr3)
plot(rderr3)
t2<-Sys.time()
t2-t1
```

